---
title: "Question 2"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

IMPORTANT! You don't need to knit this file. It is only meant for instructions.


The following will start a new project called `mypackage`. You might encounter

> New project 'myunits' is nested inside an existing project './', which is rarely a good idea.

And it is expected. Create anyway.

```{r}
library(devtools)
create_package("myunits")
```

After creating the packge project, a new RStudio window should be opened.

The goal of this package is to provide 4 functions to to convert between metric and imperial units. 

- `celsius_to_farenheit(dc)`: `9 * dc / 5 + 32`
- `farenheit_to_celsius(df)`: `(df - 32) * 5 / 9`
- `pound_to_kilogram(p)`: `p / 2.205`
- `kilogram_to_pound(kg)`: `kg * 2.205`

You could pretty follow `https://r-pkgs.org/` chapter 2. However, please skip step 2.5 `use_git` - we don't need it because the assignment Rproj is already managing the nested package Rproj.

You will need to do the followings.

- Implement the functions.
- Write documentations.
- Write simple tests using `testthat`.
- Pass the `devtools::check()` test.
- Do not forget to stage, commit and push your package at the end.
